TUGAS POLINOMIAL CHAPTER 15

### 2021-10-12 Semester I/Pemrograman dalam Sains/Minggu VIII/pr.Rmd
all gambar

```{r,echo=FALSE,message=FALSE,warning=FALSE}
f = function(x){x^4 + 4*x^2 + 7}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

Develop a Python program to evaluate the polynomial function $y = 3x^5 + 6$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the graph.

@@

@@

Develop a Python program to evaluate the polynomial function $y = 2x^6 - 1.5x^5 + 5x^4 -6.5x^3 + 6x^2 -3x + 4.5$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the relevant data.

@@

@@

# TASK 5

Develop a Python program to solve the polynomial function $y = 3x^5 + 6$.

# TASK 6

Develop a Python program to solve the polynomial function $y = 2x^6 - 1.5x^5 + 5x^4 -6.5x^3 + 6x^2 -3x + 4.5$.

>>>>

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.caption = "Gambar 15.1"}
f = function(x){x^4 + 4*x^2 + 7}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

__15.2__ Develop a Python program to evaluate the polynomial function $y = 3x^5 + 6$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the graph.

__15.5__ Develop a Python program to solve the polynomial function $y = 3x^5 + 6$.

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.caption = "Gambar 15.2"}
f = function(x){3*x^5 + 6}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@

__15.3__ Develop a Python program to evaluate the polynomial function $y = 2x^6 - 1.5x^5 + 5x^4 -6.5x^3 + 6x^2 -3x + 4.5$. Find an appropriate interval of $x$ for which the function evaluation is done and plot the relevant data.

__15.6__ Develop a Python program to solve the polynomial function $y = 2x^6 - 1.5x^5 + 5x^4 -6.5x^3 + 6x^2 -3x + 4.5$.

@@

```{r,echo=FALSE,message=FALSE,warning=FALSE,fig.retina = 10,fig.caption = "Gambar 15.3"}
f = function(x){2*x^6 - 1.5*x^5 + 5*x^4 - 6.5*x^3 + 6*x^2 - 3*x + 4.5}
a = -5
b = 5
delta = .05
gambar_fx(f,a,b,delta)
```

@@
